Comparison of Catalogs

### 2024-10-02 compare/compare.qmd
replaced scatter plot

The local volume selection has been made by taking into account galaxies with: 1. Radial velocities of $$
    V_{LG}<600 \text{ km}\cdot\text{m}^{-1}
    $$ {#eq-lcv-vel} 2. Distances of D\<11 Mpc

@@

```{python}
def scatter_plot(x, y, xerr = None, yerr = None, sigma = False, logscale = False):
    """
    Generates a scatter plot of two datasets with optional error bars, fits a linear model to the data, 
    and displays the fitted line on the plot.

    Parameters:
    - x (array-like with units): Independent variable data.
    - y (array-like with units): Dependent variable data.
    - xerr (array-like, optional): Error in the independent variable data. Default is 0.
    - yerr (array-like, optional): Error in the dependent variable data. Default is 0.

    Returns:
    None. The function displays a scatter plot with a fitted linear model.
    """
    plt.close()
    # Convert data to masked arrays, masking NaN values
    x_data = np.ma.array(x.value, mask=np.isnan(x.value))
    y_data =  np.ma.array(y.value, mask=np.isnan(y.value))

    # Handle default values for xerr and yerr
    if xerr is None:
        xerr_d = 0
    else:
        xerr_d = np.ma.array(xerr.value, mask=np.isnan(xerr))
    if yerr is None:
        yerr_d = 0
    else:
        yerr_d = np.ma.array(yerr.value, mask=np.isnan(yerr))

    # Perform linear comparison between the datasets
    c, m, r2, corr, outliers = compare_data(x, y, sigma)

    # Plot the data with error bars
    # errorbar -> needs np.ma -> no units
    if outliers is not None:
        filtered_data = np.ma.masked_array(y.value , mask = outliers)
        outlier_percentage = (np.sum(outliers) / len(outliers)) * 100

        plt.errorbar(x.value, y.value, yerr=yerr_d, c = "black", label="Clipped Data, {} ({}%)".format(np.sum(outliers), round(outlier_percentage,1)), fmt = "o", fillstyle = "none")
        plt.scatter(x[~outliers], y[~outliers],  label=f"Fitted Data, {np.sum(~filtered_data.mask)}", c = "blue")

    else:
        plt.errorbar(x_data, y_data, xerr = xerr_d, yerr = yerr_d, alpha = 0.3, c = "blue", label = "Data", fmt = ".")

    # Plot the fitted line 
    if c!=0:
        plt.plot(x, c*x.value+ m, c = "red", label = f"Fit: {y.info.name}$_H $= {c:.2f}$\cdot${x.info.name}$_L${m:+.2f}\n $R^2=$ {r2:.2f}")

    # Set plot labels
    plt.xlabel(f"LCV, {x.info.name} [{x.unit}]")
    plt.ylabel(f"HECATE, {y.info.name} [{y.unit}]")

    # Display legend
    plt.legend()

    # Show the plot
    plt.show()
    plt.close()
```

@@

```{python}
#| echo: false
ra_corr = round(compare_data(dt["Ra_1"],dt["RA_2"])[3],3)
dec_corr = round(compare_data(dt["Dec_1"],dt["DEC_2"])[3],3)
d_corr = round(compare_data(dt["Dis"],dt["D"])[3],3)
```

|  LCV  | HECATE |   Description   | Pearson Correlation \[-1,1\] |
|:-----:|:------:|:---------------:|:----------------------------:|
| Ra_1  |  RA_2  | Right Ascension |      `{python} ra_corr`      |
| Dec_1 | DEC_2  |   Declination   |     `{python} dec_corr`      |
|  Dis  |   D    |    Distance     |      `{python} d_corr`       |

::: panel-tabset
### Right Ascension

scatter_plot(dt["Ra_1"], dt["RA_2"])
```

### Declination

```{python}
scatter_plot(dt["Dec_1"], dt["DEC_2"]), 
```

```{python}
scatter_plot(dt["Dis"], dt["D"])
```
:::

@@

```{python}
rvel_corr = round(compare_data(dt["RVel"],dt["V"])[3],3)
rvel_corr_v = round(compare_data(dt["RVel"],dt["V_VIR"])[3],3)
vlg_corr = round(compare_data(dt["VLG"],dt["V"])[3],3)
vlg_corr_v = round(compare_data(dt["VLG"],dt["V_VIR"])[3],3)
cz_corr = round(compare_data(dt["cz"],dt["V"])[3],3)
cz_corr_v = round(compare_data(dt["cz"],dt["V_VIR"])[3],3)
```

@@

```{python}
scatter_plot(dt["RVel"], dt["V"], yerr = dt["E_V"])
```

@@

scatter_plot(dt["TType"], dt["T"], yerr = dt["E_T"])
```

@@

```{python}
types = dt[["T", "TType","E_T"]]
types["diff"] = dt["T"]-dt["TType"]
types = types[np.abs(types["diff"])<7]
scatter_plot(types["TType"], types["T"])
```

````{=html}
<!-- #### Normalize the scale of galaxy types

@@

types["T_norm"] = min_max_normalize(types["T"])
types["T_norm"].mask = types["T"].mask
types["TType_norm"] = min_max_normalize(types["TType"])
#types.describe()
```

@@

```{python}
types["norm_rel_diff"] = (-types["TType_norm"] + types["T_norm"])/types["T"]
sns.histplot(types["norm_rel_diff"], kde = True)
plt.xlim(-0.2,0.2)
plt.xlabel(r"$(T_{HECATE}-T_{LCV})/T_{HECATE}$")
plt.show()
```
-->
````

@@

```{python}
#| layout: [[50,50],[1]]
plt.close()
temp = dt[["inc", "INCL"]].to_pandas()

@@

temp["Percentage Change [%]"] = (-temp["inc"] + temp["INCL"])/temp["INCL"]
temp.loc[np.isinf(temp["Percentage Change [%]"]), "Percentage Change [%]"] = np.nan
sns.histplot(temp["Percentage Change [%]"], kde = True)
plt.show()
temp.describe()
```

@@

```{python}
scatter_plot(dt["a26_1"], dt["R1"])
```

@@

```{python}
dt["log_a26"] = np.log10(dt["a26_1"].data)
dt["log_a26"].unit = u.arcmin
dt["log_R1"] = np.log10(dt["R1"].data)
dt["log_R1"].unit = u.arcmin
```

```{python}
scatter_plot(dt["log_a26"], dt["log_R1"], sigma = True)
```
:::

@@

@@

::: panel-tabset
### B mag

```{python}
scatter_plot(dt["mag_B"], dt["BT"], yerr = dt["E_BT"], sigma=True)
```

### K mag

```{python}
scatter_plot(dt["Kmag"], dt["K"], yerr = dt["E_K"], sigma = True)
```

@@

temp = dt[["diff_K_mag"]].to_pandas()
c = temp["diff_K_mag"]
up_clip = c.mean() + 3*c.std()
low_clip = c.mean() - 3*c.std()
temp["Percentage Change, after 3 sigma clip [%]"] = temp["diff_K_mag"].clip(low_clip, up_clip)
temp.rename(columns={"diff_K_mag":"Percentage Change [%]"}, inplace=True)
temp.describe(percentiles=[])
```

```{python}
sns.histplot(temp, kde = True)
plt.title("Percentage change Distribution [%]")
plt.xlabel(f"K band magnitude [{dt['K'].unit}]")
plt.show()
```

\[?\]
:::

@@

@@

::: panel-tabset
### Stellar Masses Comparison

@@

```{python}
temp.rename(columns={"diff_M":"Percantage Change [%]"}, inplace = True)
```

>>>>

The local volume selection has been made by taking into account galaxies with:

1. Radial velocities of
$$
    V_{LG}<600 \text{ km}\cdot\text{m}^{-1}
$$ {#eq-lcv-vel}

2. Distances of D\<11 Mpc

@@

@@

|  LCV  | HECATE |   Description   | Pearson Correlation \[-1,1\] |
|:-----:|:------:|:---------------:|:----------------------------:|
|  Dis  |   D    |    Distance     |      `{python} round(compare_data(dt["Dis"],dt["D"])[3],3)`       |

```{python}
#| label: fig-coord-compare 
#| layout-align: center
#| fig-cap: "Comparison of the Distances"

plt.close()
fig, ax = plt.subplots()
sns.regplot(x = dt["Dis"].data, y = dt["D"].data,
                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
ax.errorbar(dt["Dis"].data, dt["D"].data, yerr = dt["E_D"].data, fmt='none', capsize=2, zorder=1, color = "blue", alpha = 0.3)
results = scipy.stats.linregress(x = dt["Dis"], y=dt["D"])
plt.xlabel("$D_{LCV}$"+" [{}]".format(dt["Dis"].unit))
plt.ylabel("$D_{HEC}$"+" [{}]".format(dt["D"].unit))
plt.legend(["Data",
            "$D_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot D_{LCV}+$"+
                f"$({results.intercept:+.2f})$"+
            f"\n $R^2 = {results.rvalue**2*100:.0f}\%$"])
plt.tight_layout()
plt.show()
```

- The average error of the distance in the HECATE catalog is $\overline{E_D} = \pm 1.6$ Mpc, so the intercept is included in the error.
- So we can assume that the Distances are the same

@@

```{python}
rvel_corr = round(compare_data(dt["RVel"],dt["V"])[3],3)
```

@@

```{python}
#| label: fig-vel-compare
#| layout-align: center
#| fig-cap: "Comparison of the Radial Velocities"
plt.close()
fig, ax = plt.subplots()
sns.regplot(x = dt["RVel"].data, y = dt["V"].data,
                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
                 line_kws=dict(alpha=0.7, color='red', linewidth=3))

ax.errorbar(dt["RVel"].data, dt["V"].data, yerr = dt["E_V"].data, fmt='none', capsize=2, zorder=1, color = "blue")
results = scipy.stats.linregress(x = dt["RVel"], y=dt["V"])
plt.xlabel("$V_{LCV}$"+" [{}]".format(dt["RVel"].unit))
plt.ylabel("$V_{HEC}$"+" [{}]".format(dt["V"].unit))
plt.legend(["Data",
            "$V_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot V_{LCV}+$"+
            f"$({results.intercept:+.2f})$"+
            f"\n $R^2 = {results.rvalue**2*100:.0f}\%$"])
plt.show()
```

- The average error of the radial velocity in the HECATE catalog is $\overline{E_V} = \pm 12\text{km}\cdot s^{-1}$ , so the intercept is included in the error.
- So we can assume that the radial velocities are the same

@@

```{python}
#| label: fig-types-compare
#| layout-ncol: 2
#| layout-align: center
#| fig-cap: "Comparison of the Types of galaxies"
#| fig-subcap: 
#| - "All the galaxies, without the correction" 
#| - "Comparison with the correction $|{T_{HECATE}-T_{LCV}}|<7$"

plt.close()
fig, ax = plt.subplots()
sns.regplot(x = dt["TType"].data, y = dt["T"].data,
                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
                 line_kws=dict(alpha=0.7, color='red', linewidth=3))

ax.errorbar(dt["TType"].data, dt["T"].data, yerr = dt["E_T"].data, fmt='none', capsize=2, zorder=1, color = "blue")
temp = dt[["TType", "T"]].to_pandas().dropna()
results = scipy.stats.linregress(x = temp["TType"],
                                y = temp["T"])
plt.xlabel("$Type_{LCV}$")
plt.ylabel("$Type_{HEC}$")
plt.legend(["Data",
            "$T_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot T_{LCV}+$"+
            f"$({results.intercept:+.2f})$"+
            f"\n $R^2 = {results.rvalue**2*100:.0f}\%$"])
plt.show()

types = dt[["T", "TType","E_T"]]
types["diff"] = dt["T"]-dt["TType"]
types = types[np.abs(types["diff"])<7]

plt.close()
fig, ax = plt.subplots()
sns.regplot(x = types["TType"].data, y = types["T"].data,
                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
                 line_kws=dict(alpha=0.7, color='red', linewidth=3))

ax.errorbar(types["TType"].data, types["T"].data, yerr = types["E_T"].data, fmt='none', capsize=2, zorder=1, color = "blue")
results = scipy.stats.linregress(x= types["TType"].data,
                                y = types["T"].data)
plt.xlabel("$Type_{LCV}$")
plt.ylabel("$Type_{HEC}$")
plt.legend(["Data",
            "$T_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot T_{LCV}+$"+
            f"$({results.intercept:+.2f})$"+
            f"\n $R^2 = {results.rvalue**2*100:.0f}\%$"])
plt.show()
```

@@

- The average uncertainty of the morphological type in the HECATE catalog is $\overline{E_T} = \pm 1.4$, so the intercept is included in the error.
- So we can assume that the Distances are the same

<!-- #### Normalize the scale of galaxy types

@@

types["T_norm"] = min_max_normalize(types["T"])
types["T_norm"].mask = types["T"].mask
types["TType_norm"] = min_max_normalize(types["TType"])
#types.describe()
```
TType

@@

```{python}
types["norm_rel_diff"] = (-types["TType_norm"] + types["T_norm"])/types["T"]
sns.histplot(types["norm_rel_diff"], kde = True)
plt.xlim(-0.2,0.2)
plt.xlabel(r"$(T_{HECATE}-T_{LCV})/T_{HECATE}$")
plt.show()
```
-->

@@

```{python}
#| layout: [[50,50]]
plt.close()
temp = dt[["inc", "INCL"]].to_pandas()

@@

temp["Percentage Change [%]"] = (-temp["inc"] + temp["INCL"])/temp["INCL"]
temp.loc[np.isinf(temp["Percentage Change [%]"]), "Percentage Change [%]"] = np.nan
sns.histplot(temp["Percentage Change [%]"], kde = True)
plt.show()
```
```{python}
temp.describe()
```

@@

```{python}
#| label: fig-axis-compare
#| layout-ncol: 2
#| layout-align: center
#| fig-cap: "Comparison of the Major Axises of the galaxies"
#| fig-subcap: 
#| - "Linear scale" 
#| - "$log_{10}$ scale"
plt.close()
fig, ax = plt.subplots()
sns.regplot(x = dt["a26_1"].data, y = dt["R1"].data,
                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
temp = dt[["a26_1","R1"]].to_pandas().dropna()
results = scipy.stats.linregress(x = temp["a26_1"], y = temp["R1"])

plt.xlabel("(Major angular diameter$)_{LCV}$")
plt.ylabel("(Semi major axis$)_{HEC}$")
plt.legend(["Data",
            "$R1_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot a_{26,LCV}$"+
            f"${results.intercept:+.2f}$"+
            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
plt.show()
dt["log_a26"] = np.log10(dt["a26_1"].data)
dt["log_R1"] = np.log10(dt["R1"].data)
plt.close()
fig, ax = plt.subplots()
p = sns.regplot(x = dt["log_a26"].data, y = dt["log_R1"].data,
                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
                 line_kws=dict(alpha=0.7, color='red', linewidth=3))

temp = dt[["log_a26","log_R1"]].to_pandas().dropna()
results = scipy.stats.linregress(x = temp["log_a26"], y = temp["log_R1"])
plt.xlabel("(Major angular diameter$)_{LCV}$"+" [{}]".format(dt["a26_1"].unit))
plt.ylabel("(Semi major axis$)_{HEC}$"+" [{}]".format(dt["R1"].unit))
plt.legend(["Data",
            "$log_{10}(R1_{HEC})=$" +f"{results.slope:.2f}"+"$\cdot log_{10}(a_{26,LCV})$"+
            f"${results.intercept:+.2f}$"+
            f"\n $R^2 = {results.rvalue**2*100:.0f}\%$"])
plt.show()
```

@@

$\overline{R_1} = 3.9$ [arcmin],  $\overline{a_{26}} = 9.3$ [arcmin], so the intercept is negligable.
$$
R_1 = 0.48\cdot a_{26}-0.34 \sim \frac{1}{2}a_{26}
$$

$$
\log(R1) = 0.89\log(a_{26})-10^{0.38} = \log(10^{-0.38}a_{26}^{0.89}) = \log(0.41\cdot a_{26}^{0.89})\Rightarrow R1\simeq \frac{a_{26}}{2}
$$

:::

@@

```{python}
#| label: fig-KLum-compare
#| fig-cap: "Comparison of the $L_K$ of the galaxies"
plt.close()
fig, ax = plt.subplots()
sns.regplot(x = dt["logKLum"], y = dt["logL_K"],
                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
temp = dt[["logKLum","logL_K"]].to_pandas().dropna()
results = scipy.stats.linregress(x = temp["logKLum"], y = temp["logL_K"])
plt.xlabel("log($L_{K, LCV} $"+"/{})".format(dt["KLum"].unit.to_string("latex")))
plt.ylabel("log($L_{K, HECATE} $"+"/{})".format(dt["KLum"].unit.to_string("latex")))
plt.legend(["Data",
            "$log(L_{K,HEC})=$" +f"{results.slope:.2f}"+"$\cdot log(L_{K,LCV})$"+
            f"${results.intercept:+.2f}$"+
            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
plt.show()
```

$$
\log(L_{K,HEC})=1.16\log(L_{K,LCV})-1.78=\log\left(\frac{{L_{K,LCV}}^{1.16}}{10^{1.78}}\right) \Leftrightarrow L_{K,HEC}=0.02\cdot{L_{K,LCV}}^{1.16}
$$

So as we can see the usage of a linear fitting is not correct here.
But we can clearly see a linear correlation.

We will use the relative difference of the two luminosities, to see if statistically they are the same:

@@

```{python}
#| label: fig-Mag-compare
#| layout-ncol: 2
#| layout-align: center
#| fig-cap: "Comparison of the Magnitudes of the galaxies"
#| fig-subcap: 
#| - "$M_B$" 
#| - "$M_K$"
#| 
plt.close()
fig, ax = plt.subplots()
sns.regplot(x = dt["mag_B"].data, y = dt["BT"].data,
                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
ax.errorbar(dt["mag_B"].data, dt["BT"].data, xerr = dt["e_mag_B"].data, yerr = dt["E_BT"].data, fmt='none', capsize=2, zorder=1, color = "blue")
temp = dt[["mag_B","BT"]].to_pandas().dropna()
results = scipy.stats.linregress(x = temp["mag_B"], y = temp["BT"])
plt.xlabel("$M_{B,LCV}$"+" [{}]".format(dt["mag_B"].unit.to_string("latex")))
plt.ylabel("$M_{B,HECATE} $"+" [{}]".format(dt["BT"].unit.to_string("latex")))
plt.legend(["Data",
            "$M_{B,HEC}=$" +f"{results.slope:.2f}"+"$\cdot M_{B,LCV}$"+
            f"${results.intercept:+.2f}$"+
            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
plt.show()

#M_K
plt.close()
fig, ax = plt.subplots()
sns.regplot(x = dt["Kmag"].data, y = dt["K"].data,
                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
ax.errorbar(dt["Kmag"].data, dt["K"].data, yerr = dt["E_K"].data, fmt='none', capsize=2, zorder=1, color = "blue")
temp = dt[["Kmag","K"]].to_pandas().dropna()
results = scipy.stats.linregress(x = temp["Kmag"], y = temp["K"])
plt.xlabel("$M_{K,LCV}$"+" [{}]".format(dt["Kmag"].unit.to_string("latex")))
plt.ylabel("$M_{K,HECATE} $"+" [{}]".format(dt["K"].unit.to_string("latex")))
plt.legend(["Data",
            "$M_{K,HEC}=$" +f"{results.slope:.2f}"+"$\cdot M_{K,LCV}$"+
            f"${results.intercept:+.2f}$"+
            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
plt.show()
```

- $M_B$: it is a 1-1 correlation, since the average error $M_{B,HECATE} = 0.4\ mag$, so the itercept is smaller than the error
- $M_K$: we need to examine it more, since the intercept is bigger than the error $M_{K,HECATE} = 0.09\ mag$

@@

temp = dt[["diff_K_mag"]].to_pandas()
c = temp["diff_K_mag"]
up_clip = c.mean() + 3*c.std()
low_clip = c.mean() - 3*c.std()
temp["Percentage Change, after 3 sigma clip [%]"] = temp["diff_K_mag"].clip(low_clip, up_clip)
temp.rename(columns={"diff_K_mag":"Percentage Change [%]"}, inplace=True)
```

```{python}
sns.histplot(temp, kde = True)
plt.title("Percentage change Distribution [%]")
plt.xlabel(f"K band magnitude [{dt['K'].unit}]")
plt.show()

sns.histplot(dt["Kmag"].data, label = "LCV")
sns.histplot(dt["K"].data, label = "HECATE")
plt.legend()
plt.xlabel(f"K band magnitude [{dt['K'].unit}]")
plt.show()
```
```{python}
temp.describe(percentiles=[])
```

\[?\] this 5\% average in the difference probably exists because of the low number of galaxies we compare, so we can ignore it.

@@

```{python}
#| label: fig-sfr-lcv
#| layout-ncol: 2
#| layout-align: center
#| fig-cap: "Comparison of the $SFR_{FUV}-SFR_{Ha} of the galaxies"
#| fig-subcap: 
#| - "Linear scale" 
#| - "Decimal logarithmic scale"

##linear
plt.close()
fig, ax = plt.subplots()
temp = lcv[["SFRHa","SFRFUV"]].to_pandas().dropna()
x = temp["SFRHa"]
y = temp["SFRFUV"]
sns.regplot(x = x, y = y,
                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
results = scipy.stats.linregress(x = x, y = y)
plt.axvline(x=1e-3, color='green', linestyle='--', linewidth=2)
plt.xlabel("$SFR_{Ha}$"+" [{}]".format(dt["SFRHa"].unit.to_string("latex")))
plt.ylabel("$SFR_{FUV} $"+" [{}]".format(dt["SFRFUV"].unit.to_string("latex")))
plt.legend(["Data",
            "$SFR_{FUV}=$" +f"{results.slope:.2f}"+"$\cdot SFR_{Ha}$"+
            f"${results.intercept:+.2f}$"+
            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
plt.show()

##log

plt.close()

x = np.log10(temp["SFRHa"])
y = np.log10(temp["SFRFUV"])
fig, ax = plt.subplots()
sns.regplot(x = x, y = y,
                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
results = scipy.stats.linregress(x = x, y = y)
plt.axvline(x=-3, color='green', linestyle='--', linewidth=2)

plt.xlabel("$log(SFR_{Ha})$"+" [{}]".format(dt["logSFR_HEC"].unit.to_string("latex")))
plt.ylabel("$log(SFR_{FUV})$"+" [{}]".format(dt["logSFR_HEC"].unit.to_string("latex")))
plt.legend(["Data",
            "$log(SFR_{FUV})=$" +f"{results.slope:.2f}"+"$\cdot log(SFR_{Ha})$"+
            f"${results.intercept:+.2f}$"+
            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
plt.show()
```

The SFR according to @kroupaConstraintsStarFormation2020, can be calculated from the mean of SFR from the Ha and FUV, for $SFR>10^{-3}\ M_\odot\, yr^{-1}$. As we can see from the plots @fig-sfr-lcv it is a good aproximation for all SFR's

$$
SFR = \frac{SFR_{FUV}+SFR_{H\alpha}}{2}, \text{if both exist, else: } SFR = SFR_i,\ i= FUV,\, H\alpha
$$

```{python}
sfr_fuv = dt['SFRFUV']
sfr_ha = dt['SFRHa']

dt["SFR_t"] =np.log10(np.nanmean([sfr_fuv, sfr_ha], axis=0))
dt["SFR_t"].unit = dt["SFRFUV"].unit
```

```{python}
#| label: fig-SFR-compare
#| layout-ncol: 2
#| layout-align: center
#| fig-cap: "Comparison of the SFR's of the galaxies"
#| fig-subcap: 
#| - "Linear scale" 
#| - "Decimal logarithmic scale"

##linear
plt.close()
fig, ax = plt.subplots()
temp = dt[["SFR_t","logSFR_HEC"]].to_pandas().dropna()
temp = temp[temp["SFR_t"]>-3]
sns.regplot(x = 10**temp["SFR_t"], y = 10**temp["logSFR_HEC"],
                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
results = scipy.stats.linregress(x = 10**temp["SFR_t"], y = 10**temp["logSFR_HEC"])
plt.xlabel("$SFR_{LCV}$"+" [{}]".format(dt["SFR_t"].unit.to_string("latex")))
plt.ylabel("$SFR_{HECATE} $"+" [{}]".format(dt["SFR_t"].unit.to_string("latex")))
plt.legend(["Data",
            "$SFR_{HEC}=$" +f"{results.slope:.2f}"+"$\cdot SFR_{LCV}$"+
            f"${results.intercept:+.2f}$"+
            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
plt.show()

##log

plt.close()
fig, ax = plt.subplots()
temp = dt[["SFR_t","logSFR_HEC"]].to_pandas().dropna()
temp = temp[temp["SFR_t"]>-3]
sns.regplot(x = temp["SFR_t"], y = temp["logSFR_HEC"],
                 scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'),
                 line_kws=dict(alpha=0.7, color='red', linewidth=3))
results = scipy.stats.linregress(x = temp["SFR_t"], y = temp["logSFR_HEC"])
plt.xlabel("$log(SFR_{LCV})$"+" [{}]".format(dt["logSFR_HEC"].unit.to_string("latex")))
plt.ylabel("$log(SFR_{HECATE})$"+" [{}]".format(dt["logSFR_HEC"].unit.to_string("latex")))
plt.legend(["Data",
            "$log(SFR_{HEC})=$" +f"{results.slope:.2f}"+"$\cdot log(SFR_{LCV})$"+
            f"${results.intercept:+.2f}$"+
            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
plt.show()
```

?EXPLANATION? this low correlation maybe comes from the inaccuracy/approximation of @kroupaConstraintsStarFormation2020

@@

::: panel-tabset

### Stellar Masses Comparison

```{python}
#| label: fig-Mass-compare
#| fig-cap: "Comparison of the Stellar Masses of the galaxies"

plt.close()
fig, ax = plt.subplots()
temp = dt[["logStellarMass","logM_HEC"]].to_pandas().dropna()
x = temp["logStellarMass"]
y = temp["logM_HEC"]
sns.regplot(x = x, y = y, 
                scatter_kws=dict(alpha=0.5, color='blue', edgecolors='white'), 
                line_kws=dict(alpha=0.7, color='red', linewidth=3))
results = scipy.stats.linregress(x = x, y = y)
plt.xlabel("$log(M_{*,LCV})$"+" [{}]".format(dt["logM_HEC"].unit.to_string("latex")))
plt.ylabel("$log(M_{*,HECATE} )$"+" [{}]".format(dt["logM_HEC"].unit.to_string("latex")))
plt.legend(["Data",
            "$log(M_{*,HEC})=$" +f"{results.slope:.2f}"+"$\cdot log(M_{*,LCV})$"+
            f"${results.intercept:+.2f}$"+
            f"\n $R^2 = {results.rvalue**2*100:.2f}\%$"])
plt.show()

```
```{python}

@@

$$
\log{M_{*,HECATE}}=1.07\cdot\log{M_{*,LCV}}-0.69, \text{ but } \log{M_*}>6\Rightarrow M_{*,HEC}\sim M_{*,LCV}
$$

As we can see the aproximation of Mass/Light=const.=0.6 is a pretty good approximation, for the calculation of $\log(M_*/M_\odot)$, especially for high-mass galaxies
